% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

\author{}
\date{}

\begin{document}

Assignment \#3

\begin{quote}
Sabancı University\\
Computer Science \& Engineering\\
CS419 - Digital Image and Video Analysis\\
Fall semester 2025 - 2026

\textbf{1} \textbf{Goal}

You are expected to implement a segmentation pipeline from scratch.

\textbf{2} \textbf{Dataset}

You will use a microscopy cell dataset from 20221. This google drive
link2contains various images (images folder) and their pixel level
annotations (labels folder) as 16bit tiff files.

\textbf{3} \textbf{Task}

You are expected to develop a segmentation pipeline that given a color
image from the aforemen-tioned directory, produces as output a new
grayscale image of the same size, where every pixel of every cell (as
defined by the annotations) is set to a different scalar pixel value;
e.g. let's say an image contains 3 cells. Then the output will set all
the pixels of cell-1 to 1, all the pixels of cell-2 to 2, all the pixels
of cell-3 to 3, and all the background pixels will be set to 0.

You are free to propose any method you want, as long as it is not about
deep learning. \textbf{The proposed method must be using at its core at
least one of the segmentation methods treated in class.} Note that this
is a challenging dataset! I expect you to study comprehensively the
effect of the parameters of your method on segmentation performance and
to investigate its robustness. How good is it? When is it performing
well? When is it performing bad? And why?

\textbf{4} \textbf{Deliverables}

1. Your code as a python file, or as a python notebook. Make sure its
name is your student id.

2. A report in pdf format, prepared according to the IEEE double column
conference template. Your report should elaborate your method, and
justify its design decisions. It must also contain visuals of successful
segmentations and failures. Report your numerical scores using at least
10 images of your choice from the dataset.

\textbf{5} \textbf{Evaluation}
\end{quote}

Performance will be measured in terms of pixel level F1 score (as \%)
and intersection over union

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 2\tabcolsep) * \real{0.5000}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 2\tabcolsep) * \real{0.5000}}@{}}
\toprule()
\begin{minipage}[b]{\linewidth}\raggedright
scores (\emph{∈}{[}0\emph{,} 1{]}).
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
\begin{quote}
Your submission will be tested with arbitrary images of our choice from
the
\end{quote}
\end{minipage} \\
\midrule()
\endhead
\bottomrule()
\end{longtable}

\begin{quote}
1https://neurips22-cellseg.grand-challenge.org/dataset/\\
2https://drive.google.com/drive/folders/1OIGdxeyBFX73f9rIdq1AdzblY2Y9Jc5g
\end{quote}

1

provided directory. The report will be evaluated in terms of
comprehensiveness, design quality and justifications.

\textbf{6} \textbf{Instructions}

\begin{quote}
1. Integrity: plagiarism is strongly prohibited and will lead to failure
of this course.

2. Questions: post your questions to the ``questions'' forum at the
course's sucouse page.
\end{quote}

Good luck.

2

\end{document}
